### 2015-07-10 narrative/intro.tex

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of the users who want to read in the data from their
simulations, and then operate on this data and possibly write data, we see
that in general these users will be running on much less compute resources
than the users who are running the simulation. One of the important aspects
of this class of user is that they want a reduction of latency and they
require a certain amount of QoS as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data.

>>>>

\paragraph{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of reading, this project will look at both
simulation restart and post-processing. For the former case,
we will allow both traditional file-based approach leveraging fast storage tier
such as NVRAM (non-volatile RAM), and memory-based approach via retrieving
data directly from NVRAM. For the latter case,
an important aspect is that they want a reduction of latency and they
require a certain amount of QoS as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data.
